\section{Work Experience}

\entry{08/2023 -- 10/2025}
{Senior Software Engineer}
{Village}
{
Responsibilities:
\begin{itemize}
	\item Collaborated with a small, talented team of developers and designers to build a high-impact platform connecting children with extracurricular opportunities across the U.S.
	\item Partnered closely with Product to translate ideas into intuitive, accessible, and visually engaging user experiences.
	\item Delivered high-quality, maintainable solutions using technologies such as Next.js, TypeScript, Vitest, Radix UI, GraphQL and Styled Components.
	\item Wrote comprehensive unit tests (Vitest) and end-to-end tests (Playwright) to ensure product reliability and scalability.
\end{itemize}

\vspace{0.1cm}
Key Strengths:
\begin{itemize}
	\item Experienced in agile environments, contributing to fast-moving projects and collaborating effectively in small, cross-functional teams.
	\item Strong focus on both code quality and user experience, balancing performance, maintainability, and design consistency.
\end{itemize}
}

\entry{06/2022 -- 08/2023}
{Full Stack Engineer}
{Howdy\texttrademark{} (Uruguay)}
{
Responsibilities:
\begin{itemize}
	\item Successfully collaborated on numerous cross-functional Agile teams, assuring optimal software development procedures.
	\item Demonstrated a strong dedication to enhancing code quality consistently and putting best practices into use to promote excellence in software development.
	\item Improved user interface (UI) and user experience (UX) by using a comprehensive development strategy.
	\item Delivered high-quality solutions by utilizing a variety of technologies, such as React, Next.js, Jest, Express, Material UI, and Tailwind CSS.
\end{itemize}

\vspace{0.1cm}
Key Characteristics:
\begin{itemize}
	\item Experience working in agile development environments and successfully completing projects in nimble, friendly teams.
	\item Adept at spotting opportunities to improve code quality and putting established best practices into effect.
	\item Demonstrated capacity to offer benefits outside of coding, actively contributing to improving UX and UI design.
\end{itemize}
}

\entry{02/2022 -- 07/2022}
{Frontend Engineer}
{KAIZEN Softworks (Montevideo, Uruguay)}
{
Working in an Agile-driven development team, focusing on value over time, and people over processes.
\begin{itemize}
	\item Interacting with stakeholders daily.
	\item Working with the design teams to improve UX/UI.
	\item Producing responsive web apps, which follow strict coding guidelines to improve their quality and value.
	\item Increasing Lighthouse score from 75 to 97.
	\item Working with technologies like Next.js, Tailwind, SASS, and Jest.
\end{itemize}
}

\entry{03/2020 -- 02/2022}
{Full Stack Engineer}
{KAIZEN Softworks (Montevideo, Uruguay)}
{
Worked on a mid-scale project, using React Native for the mobile app, React to build the frontend side of it, and .NET to implement the backend.

\vspace{0.1cm}
Improved the value of an already created project, by not only focusing on the code itself but also thriving to improve relationships with the stakeholders.

\vspace{0.1cm}
Focused on documenting practices for future team members, such as environment settings, technologies used, and deployments to different environments. As well as publishing the mobile app on App Store and Google Store.
}
